Preliminary Draft

### 2021-07-26 article/draft.tex
updates to the figures function + linked tex figures to parent folder

\begin{figure}[h]
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.3]{./img/fb/fig1_fb.png}
		%\end{multicols}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
	%\end{multicols}
\caption{Left Panel: number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Right Panel: number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

\begin{figure}[h]
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{./img/oann/fig1_oann.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.26]{./img/oann/fig2_oann.png} 
	%\end{multicols}
	\caption{Left Panel: Number of YouTube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Right Panel: accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

@@

%\smallskip
\begin{figure}[h]
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.35]{./img/tony/fig1_tony.png}
		%\end{multicols}
		%\begin{multicols}{1}
			\includegraphics[scale=0.34]{./img/tony/fig2_tony.png}
		%\end{multicols}
	\caption{Left Panel: Number of YouTube videos uploaded each day by the YouTube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020. Right Panel: accumulated view counts for videos uploaded by the same YouTube channel. The date corresponds to the videos’  publishing date. 
}
	\label{fig1_tony}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.4]{../figure/facebook_crowdtangle_trump.png}
		%\end{multicols}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{../figure/lifesite.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.34]{./img/lifesite_rolling_7_lifesite.jpg}
	%\end{multicols}
\caption{Left Panel: number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Right Panel: number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

\begin{figure}[h]
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{../figure/OANN_videos_yt.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{../figure/OANN_views_yt.png} 
	%\end{multicols}
	\caption{Left Panel: Number of YouTube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Right Panel: accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

@@

%\smallskip
\begin{figure}[h]
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.26]{../figure/Tony_Heller_videos_yt.png}
		%\end{multicols}
		%\begin{multicols}{1}
			\includegraphics[scale=0.26]{../figure/Tony_Heller_views_yt.png}
		%\end{multicols}
	\caption{Left Panel: Number of YouTube videos uploaded each day by the YouTube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020. Right Panel: accumulated view counts for videos uploaded by the same YouTube channel. The date corresponds to the videos’  publishing date. 
}
	\label{fig1_tony}
\end{figure}
